### 2021-07-02 doc/src/MSLevel.tex
Added comments about the default priority of interrupt 0

@@

@@

>>>>

\begin{commentary}
If the {\RISCV} Privileged Architecture defines interrupt~0, the
Advanced Interrupt Architecture needs it to have a default priority
lower than certain external interrupts.
See Sections \ref{sec:mtopi} and~\ref{sec:stopi} on CSRs \z{mtopi} and
\z{stopi}.
\end{commentary}

@@

\begin{commentary}
To ensure that \z{mtopi} is never zero when an interrupt is pending
and enabled for machine level, if major interrupt~0 can trap to
\hbox{M-mode}, it must have a default priority lower than a machine
external interrupt.
\end{commentary}

@@

\begin{commentary}
To ensure that \z{stopi} is never zero when an interrupt is pending
and enabled for supervisor level, if major interrupt~0 can trap to
\hbox{S-mode}, it must have a default priority lower than a supervisor
external interrupt.
\end{commentary}
